{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-17 paper/paper.tex
use package asmth and set defintion as standard
added main theorem

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{bussproofs}

\pagestyle{plain}
\bibliographystyle{alpha}

@@

\subsection{Soundness}
\label{sec:soundness}
\subsection{Instantiation}
\label{sec:instantiation}

>>>>

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{bussproofs}
\usepackage{amsthm}

\theoremstyle{definition}
\pagestyle{plain}
\bibliographystyle{alpha}

@@

\subsection{Soundness}
\label{sec:soundness}
The framework is now complete, but the proof of the connection between the
type system and the noninterference property is still outstanding. The full
proof is not part of the paper and I will only sketch the most important
parts.

The goal is to proof the following theorem:

\begin{theorem}
If the scheduler is secure and $se, \mathcal{S} \vdash P$, then P is noninterfering
\end{theorem}

\subsection{Instantiation}
\label{sec:instantiation}
